### 2020-07-19 ChapterResults/chapterResults.tex
Update: Add a category for each of the speed tolerances chosen

The first experiment conducted was the varying speed experiment. In this experiment the speed of each of the two objects was varied from $1m\mathord{\cdot}s^{-1}$ to double the the following tolerances: $16m\mathord{\cdot}s^{-1}$; $32m\mathord{\cdot}s^{-1}$ and $48m\mathord{\cdot}s^{-1}$. Increments of $1m\mathord{\cdot}s^{-1}$ were used and the whole experiment repeated $50$ times.

>>>>

The first experiment conducted was the varying speed experiment. In this experiment the speed of each of the two objects was varied from $1m\mathord{\cdot}s^{-1}$ to double the the following tolerances: $16m\mathord{\cdot}s^{-1}$; $32m\mathord{\cdot}s^{-1}$ and $48m\mathord{\cdot}s^{-1}$. Increments of $1m\mathord{\cdot}s^{-1}$ were used and the whole experiment repeated $50$ times. In these experiments it is assumed 1 unit is 1 metre. The speed tolerances chosen represent categories of typical fast moving objects in games. The categories selected were: slow-moving vehicles ($16m\mathord{\cdot}s^{-1}$); fast-moving/motorway-speed vehicles ($32m\mathord{\cdot}s^{-1}$); and racing vehicles ($48m\mathord{\cdot}s^{-1}$).
